---
title: "RInside"
author: "Shaojun Zhang"
date: "November 12, 2015"
output: beamer_presentation
slide_level: 1
---

## Install
```{r, eval=FALSE}
install.packages(c("Rcpp", "RInside"))
```
If it doesn't work, try building from source or asking on Stack Overflow.

## C++ to R
```{r engine='Rcpp', eval = FALSE}
R["a"] = x;
R.assign(x, "a");
```
- a is the variable we want to create in R and assign value x
- x can be all C++ basic types (e.g. int, double, boolean, string), STL containers (e.g. vector, map, set) or Rcpp containers (e.g. NumericVector, NumericMatrix)

## R to C++
- R.parseEvalQ() evaluates string, ignoring any returns
- R.parseEvalQNT() evaluates string without throwing exceptions, ignoring any returns
- R.parseEval() evalulates string, then return the value of the last assignment
- R.parseEvalNT() evalulates string without throwing exceptions
```{r engine='Rcpp', eval = FALSE}
R.parseEvalQ(cmd);
type x = Rcpp::as<type>(R.parseEval(cmd));
Rcpp::type x((SEXP) R.parseEval(cmd));
type x = Rcpp::as<type>R["a"];
```

## How to use?
- write cpp file
- write Makefile
- build and execute
